ms2

### 2017-06-21 ms2/ms2.Rmd
moving to HRR

```{r}
x = abg %>% 
  select(bug, drug_group, state) %>%
  distinct() %>%
  count(bug, drug_group) %>% ungroup() %>% rename(n_places=n)
results %>% filter(model=='spearman') %>%
  left_join(x, by=c('bug', 'drug_group')) %>%
  ggplot(aes(x=n_places, y=estimate)) +
  geom_point()
```

@@

## MSSA and clindamycin

```{r mssa_clinda}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='MSSA', drug_group=='clindamycin') %>%
  ggplot(aes(x=cpb, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  xlab('clindamycin claims per beneficiary') + ylab('mean percent nonsusceptible MSSA isolates') +
  theme_minimal()
```

>>>>

HRR spearman:

```{r hrr_spearman_interval}
hrr_results %>%
  filter(model=='spearman') %>%
  interval_plot() +
  ylab("Spearman's rho")
```

```{r, eval=FALSE}
# Used this to show that there's a correlation between
# strength of correlation and amount of data
x = abg %>% 
  select(bug, drug_group, state) %>%
  distinct() %>%
  count(bug, drug_group) %>% ungroup() %>% rename(n_places=n)
results %>% filter(model=='spearman') %>%
  left_join(x, by=c('bug', 'drug_group')) %>%
  ggplot(aes(x=n_places, y=estimate)) +
  geom_point()
```

@@

## S. aureus and clindamycin

```{r staph_clinda}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='S. aureus', drug_group=='clindamycin') %>%
  ggplot(aes(x=cpb, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  xlab('clindamycin claims per beneficiary') + ylab('mean percent nonsusceptible S. aureus isolates') +
  theme_minimal()
```
